### 2021-02-23 architecture.tex
s pripadnou kompresi tez pomuze (mozno opet zacomentovat a tim ziskat llncs default)

The following formula captures the complete update of embedding of node $d$ by layer $l$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
$$
\todo{FB: Include LayerNorm and Residual if we end up using them.}
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
%\todo{FB: Mention inspiration: Transformer. See Straka's slides.}

@@

\subsubsection{Precedence cost}
We extend the notion of cost from symbols to precedences
by summing up the symbol costs
weighted by their positions in the given precedence $\pi$:
$$
C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))
% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
$$
$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
independent of the signature size $n$:
\begin{align*}
\mathbb{E}_\pi [C(\pi)]
&= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))} \\
&= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
&= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)] \\
&= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)] \\
&= \mathbb{E}_i [c(i)]
\end{align*}
\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$. Keep in mind that $\inv{\pi}$ must be updated as well. The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$. How about using $(\inv{\pi})_i$? We may also omit the inversion completely.}

>>>>

The following formula captures the complete update of embedding of node $d$ by layer $l$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
$$

\todo{FB: Include LayerNorm and Residual if we end up using them.}
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
%\todo{FB: Mention inspiration: Transformer. See Straka's slides.}

@@

\subsubsection{Precedence cost}
We extend the notion of cost from symbols to precedences
by summing up the symbol costs
weighted by their positions in the given precedence $\pi$:
$$
C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
$$
$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
independent of the signature size $n$:
\begin{align*}
\mathbb{E}_\pi [C(\pi)]
&= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))} \\
&= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
&= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)] \\
&= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)] \\
&= \mathbb{E}_i [c(i)]
\end{align*}

\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$. Keep in mind that $\inv{\pi}$ must be updated as well. The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$. How about using $(\inv{\pi})_i$? We may also omit the inversion completely.}

### 2021-02-23 main.tex
s pripadnou kompresi tez pomuze (mozno opet zacomentovat a tim ziskat llncs default)

>>>>

% Some mild shrinkage:

% for Section and subsection headings:
%% Save the class definition of \subparagraph
\let\llncssubparagraph\subparagraph
%% Provide a definition to \subparagraph to keep titlesec happy
\let\subparagraph\paragraph
%% Load titlesec
\usepackage{titlesec}
%% Revert \subparagraph to the llncs definition
\let\subparagraph\llncssubparagraph
\titlespacing*{\subsection}
  {0pt}{0.9\baselineskip}{0.8\baselineskip}

% For figures
% https://tex.stackexchange.com/questions/60477/remove-space-after-figure-and-before-text
\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float at the top and text
\setlength{\floatsep}{0.3\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between two floats at the top
\setlength{\intextsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float in text and text
